---
title: Thesis Survey Data analysis
output: pdf_document
author: Ashkan Taravati
---
This data analysis is conducted using the R language and the data is stored in a .csv file.
```{r include=FALSE}
library(GGally)
library(ggplot2)

```

# Dataset
```{r echo=FALSE}
data = read.csv("data.csv")

data
```

\pagebreak

# General Analysis


## Correlogram of core variables
```{r echo=FALSE}
core_data <- subset(data, select=-c(team,org,response_rate,response_count))
ggpairs(core_data,progress=FALSE,title="Pairwise Correlation Matrix")
```

\pagebreak

## Multiple Linear Regression of all variables against team effectiveness
```{r echo=FALSE}
full_lm <- lm(effectiveness ~ ., data=core_data)
print(summary(full_lm))
```

\pagebreak

# Hypothesis testing

## Hypothesis No. 1
H1: Team Overconfidence has a negative effect on team coordination
```{r echo=FALSE} 
lm_overconfidence_coordination = lm(formula = overconfidence ~ coordination, data = data)
rep.h1 <- summary(lm_overconfidence_coordination)

print(rep.h1)

plot( data$coordination ~ data$overconfidence, data = data)
abline(lm_overconfidence_coordination)
ggplot(data, aes(x=coordination, y=overconfidence)) + geom_point()
```

\pagebreak

## Hypothesis No. 2
H2: Team Overconfidence has a positive effect on team effectiveness
```{r echo=FALSE}
lm_effectiveness_coordination = lm(formula = effectiveness ~ coordination, data = data)
rep.h2 <- summary(lm_effectiveness_coordination)
print(rep.h2)
plot(data$effectiveness ~ data$coordination, data = data)
abline(lm_effectiveness_coordination)
ggplot(data, aes(x=effectiveness, y=coordination)) + geom_point()
```

\pagebreak

## Hypothesis No. 3
H3: Team Overconfidence has a positive effect on team response rate
```{r echo=FALSE}
data$inter<-data$overconfidence*data$voice_behavior
lm_voice_coordination = lm(formula = coordination ~ overconfidence + voice_behavior + inter , data = data)
rep.h3 <- summary(lm_voice_coordination)
rep.h3
plot(data$coordination ~ data$overconfidence, data = data)
abline(lm_voice_coordination)
ggplot(data, aes(x=coordination, y=overconfidence)) + geom_point()
```

\pagebreak

# Extra Hypotheses

## Hypothesis No. 1 - a
Hx1a: Team Overconfidence has a negative effect on team Effectiveness
```{r echo=FALSE}
lm_overconfidence_effectiveness = lm(formula =  effectiveness ~ overconfidence, data = data)
rep.hx1a <- summary(lm_overconfidence_effectiveness)
print(rep.hx1a)
plot(data$effectiveness ~ data$overconfidence, data = data)
abline(lm_overconfidence_effectiveness)
ggplot(data, aes(x=effectiveness, y=overconfidence)) + geom_point()
```

\pagebreak

## Hypothesis No. 1 - b
Hx1b: Team Overconfidence has a reverse effect on team Effectiveness mediated by team Coordination
```{r echo=FALSE}
data$inter2<-data$overconfidence*data$coordination

lm_overconfidence_effectiveness_coordination = lm(formula =  effectiveness ~ overconfidence + coordination + inter2, data = data) 
rep.hx1b <- summary(lm_overconfidence_effectiveness_coordination)
print(rep.hx1b)
plot(data$effectiveness ~ data$overconfidence, data = data)
abline(lm_overconfidence_effectiveness_coordination)
ggplot(data, aes(x=effectiveness, y=overconfidence)) + geom_point()
```
