---
title: Thesis Survey Data analysis
output: 
  pdf_document:
    toc: TRUE
author: Ashkan Taravati
---
```{r include=FALSE}
library(GGally)
library(ggplot2)
library(equatiomatic)
teams = read.csv("teams.csv")
responses = read.csv("responses.csv")
```



\pagebreak

# Hypothesis Testing

## Hypothesis No. 1
H1: Team Overconfidence has a negative effect on team coordination
```{r echo=FALSE} 
lm_overconfidence_coordination = lm(formula = coordination ~ overconfidence, data = teams)
rep.h1 <- summary(lm_overconfidence_coordination)

print(rep.h1)

plot( teams$coordination ~ teams$overconfidence, data = teams)
abline(lm_overconfidence_coordination)
ggplot(teams, aes(x=coordination, y=overconfidence)) + geom_point()
```

\pagebreak

## Hypothesis No. 2
H2: Team Coordination has a positive effect on team effectiveness
```{r echo=FALSE}
lm_effectiveness_coordination = lm(formula = effectiveness ~ coordination, data = teams)
rep.h2 <- summary(lm_effectiveness_coordination)
print(rep.h2)
plot(teams$effectiveness ~ teams$coordination, data = teams)
abline(lm_effectiveness_coordination)
ggplot(teams, aes(x=effectiveness, y=coordination)) + geom_point()
```

\pagebreak

## Hypothesis No. 3
H3: Voice Behavior has a moderator effect on the relationship between overconfidence and team coordination
```{r echo=FALSE}
inter<-teams$overconfidence*teams$voice_behavior
teams_voice_interaction = data.frame(teams, inter)
lm_voice_coordination = lm(formula = coordination ~ overconfidence + voice_behavior + inter , data = teams_voice_interaction)
rep.h3 <- summary(lm_voice_coordination)
rep.h3
plot(teams_voice_interaction$coordination ~ teams_voice_interaction$overconfidence, data = teams_voice_interaction,xlab="Team Coordination", ylab="Team Overconfidence")
abline(lm(coordination ~ overconfidence,data=teams_voice_interaction), col="blue")
abline(lm_voice_coordination, col="red")
ggplot(teams_voice_interaction, aes(x=coordination, y=overconfidence)) + geom_point()
```

\pagebreak

# Extra Hypotheses

## Hypothesis No. 1 - a
Hx1a: Team Overconfidence has a negative effect on team Effectiveness
```{r echo=FALSE}
lm_overconfidence_effectiveness = lm(formula =  effectiveness ~ overconfidence, data = teams)
rep.hx1a <- summary(lm_overconfidence_effectiveness)
print(rep.hx1a)
plot(teams$effectiveness ~ teams$overconfidence, data = teams)
abline(lm_overconfidence_effectiveness)
ggplot(teams, aes(x=effectiveness, y=overconfidence)) + geom_point()
```

\pagebreak

## Hypothesis No. 1 - b
Hx1b: Team Overconfidence has a reverse effect on team Effectiveness mediated by team Coordination
```{r echo=FALSE}
inter2<-teams$overconfidence*teams$coordination
teams_overconfidence_interaction = data.frame(teams, inter2)

lm_overconfidence_effectiveness_coordination = lm(formula =  effectiveness ~ overconfidence + coordination + inter2, data = teams_overconfidence_interaction) 
rep.hx1b <- summary(lm_overconfidence_effectiveness_coordination)
print(rep.hx1b)
plot(teams_overconfidence_interaction$effectiveness ~ teams_overconfidence_interaction$overconfidence, data = teams_overconfidence_interaction)
abline(lm_overconfidence_effectiveness_coordination)
ggplot(teams_overconfidence_interaction, aes(x=effectiveness, y=overconfidence)) + geom_point()
```
\pagebreak

# Analysis of Internal Reliability
``` {r include=FALSE}
library(ltm)

eff_survey <- subset(responses, select=c(eff_q1,eff_q2,eff_q3,eff_q4,eff_q5,eff_q6,eff_q7,eff_q8,eff_q9,eff_q10))
coord_survey <- subset(responses, select=c(coord_q1,coord_q2,coord_q3,coord_q4,coord_q5))
voice_survey <- subset(responses, select=c(voice_q1,voice_q2,voice_q3,voice_q4,voice_q5,voice_q6))
ovconf_survey <- subset(responses, select=c(ovconf_q1h,ovconf_q1l,ovconf_q2h,ovconf_q2l,ovconf_q3h,ovconf_q3l,ovconf_q4h,ovconf_q4l,ovconf_q5h,ovconf_q5l,ovconf_q6h,ovconf_q6l,ovconf_q7h,ovconf_q7l,ovconf_q8h,ovconf_q8l,ovconf_q9h,ovconf_q9l,ovconf_q10h,ovconf_q10l))
```

Cronbach's Alpha is used to determine the reliability of the survey used for each variable.

## Team Effectiveness
```{r echo=FALSE}
cronbach.alpha(eff_survey, CI=TRUE)
```

### Team Commitment
```{r echo=FALSE}
commit_survey <- eff_survey[1:5]
cronbach.alpha(commit_survey, CI=TRUE)

```

### Team Performance
```{r echo=FALSE}
perf_survey <- eff_survey[6:10]
cronbach.alpha(perf_survey, CI=TRUE)

```


## Team Coordination
```{r echo=FALSE}
cronbach.alpha(coord_survey, CI=TRUE)
```

## Team Voice Behavior
```{r echo=FALSE}
cronbach.alpha(voice_survey, CI=TRUE)
```

## Overconfidence
```{r echo=FALSE}
cronbach.alpha(ovconf_survey, CI=TRUE)
```

\pagebreak

# Multiple Regression Backward Elimination of Variables
```{r echo=FALSE}
core_data <- subset(teams, select=-c(team,org,response_rate,response_count))

```

```{r echo=FALSE}
final_model <- lm(effectiveness ~ ., data=core_data)
extract_eq(final_model, wrap = TRUE,use_coefs = TRUE)

```


## Stage 0: All Variables Included

### Initial
```{r echo=FALSE}
ggpairs(core_data,progress=FALSE,title="Pairwise Correlation Matrix")
full_lm <- lm(effectiveness ~ ., data=core_data)
print(summary(full_lm))
```
\pagebreak

### Eliminating Overconfidence
```{r echo=FALSE}
core_data_except_overconfidence <- subset(core_data, select=-c(overconfidence))
all_except_overconfidence <- lm(effectiveness ~ ., data=core_data_except_overconfidence)
print(summary(all_except_overconfidence))
```
\pagebreak

### Eliminating Coordination
```{r echo=FALSE}
core_data_except_coordination <- subset(core_data, select=-c(coordination))
all_except_coordination <- lm(effectiveness ~ ., data=core_data_except_coordination)
print(summary(all_except_coordination))
```
\pagebreak

### Eliminating Voice Behavior
```{r echo=FALSE}
core_data_except_voice_behavior <- subset(core_data, select=-c(voice_behavior))
all_except_voice_behavior <- lm(effectiveness ~ ., data=core_data_except_voice_behavior)
print(summary(all_except_voice_behavior))
```
\pagebreak

### Eliminating History
```{r echo=FALSE}
core_data_except_history <- subset(core_data, select=-c(history))
all_except_history <- lm(effectiveness ~ ., data=core_data_except_history)
print(summary(all_except_history))
```
\pagebreak

### Eliminating Tenure
```{r echo=FALSE}
core_data_except_tenure <- subset(core_data, select=-c(tenure))
all_except_tenure <- lm(effectiveness ~ ., data=core_data_except_tenure)
print(summary(all_except_tenure))
```
\pagebreak

### Eliminating Age
```{r echo=FALSE}
core_data_except_age <- subset(core_data, select=-c(age))
all_except_age <- lm(effectiveness ~ ., data=core_data_except_age)
print(summary(all_except_age))
```
\pagebreak

### Eliminating Team Size
```{r echo=FALSE}
core_data_except_team_size <- subset(core_data, select=-c(team_size))
all_except_team_size <- lm(effectiveness ~ ., data=core_data_except_team_size)
print(summary(all_except_team_size))
```
\pagebreak

### Outcome

Overconfidence is the least correlated with the Effectiveness, so it is eliminated.

```{r echo=FALSE}
core_data <- subset(core_data, select=-c(overconfidence))

```

```{r echo=FALSE}
final_model <- lm(effectiveness ~ ., data=core_data)
extract_eq(final_model, wrap = TRUE,use_coefs = TRUE)

```
\pagebreak

## Stage 1: Overconfidence is Eliminated

### Initial
```{r echo=FALSE}
ggpairs(core_data,progress=FALSE,title="Pairwise Correlation Matrix")
full_lm <- lm(effectiveness ~ ., data=core_data)
print(summary(full_lm))
```

\pagebreak

### Eliminating Coordination
```{r echo=FALSE}
core_data_except_coordination <- subset(core_data, select=-c(coordination))
all_except_coordination <- lm(effectiveness ~ ., data=core_data_except_coordination)
print(summary(all_except_coordination))
```

\pagebreak

### Eliminating Voice Behavior
```{r echo=FALSE}
core_data_except_voice_behavior <- subset(core_data, select=-c(voice_behavior))
all_except_voice_behavior <- lm(effectiveness ~ ., data=core_data_except_voice_behavior)
print(summary(all_except_voice_behavior))
```

\pagebreak

### Eliminating History
```{r echo=FALSE}
core_data_except_history <- subset(core_data, select=-c(history))
all_except_history <- lm(effectiveness ~ ., data=core_data_except_history)
print(summary(all_except_history))
```
\pagebreak

### Eliminating Tenure
```{r echo=FALSE}
core_data_except_tenure <- subset(core_data, select=-c(tenure))
all_except_tenure <- lm(effectiveness ~ ., data=core_data_except_tenure)
print(summary(all_except_tenure))
```

\pagebreak

### Eliminating Age
```{r echo=FALSE}
core_data_except_age <- subset(core_data, select=-c(age))
all_except_age <- lm(effectiveness ~ ., data=core_data_except_age)
print(summary(all_except_age))
```

\pagebreak

### Eliminating Team Size
```{r echo=FALSE}
core_data_except_team_size <- subset(core_data, select=-c(team_size))
all_except_team_size <- lm(effectiveness ~ ., data=core_data_except_team_size)
print(summary(all_except_team_size))
```
\pagebreak

### Outcome

Age has the least correlation with the Effectiveness, so it is eliminated.

```{r echo=FALSE}
core_data <- subset(core_data, select=-c(age))

```
```{r echo=FALSE}
final_model <- lm(effectiveness ~ ., data=core_data)
extract_eq(final_model, wrap = TRUE,use_coefs = TRUE)

```
\pagebreak


## Stage 2: Age is Eliminated

### Initial
```{r echo=FALSE}
ggpairs(core_data,progress=FALSE,title="Pairwise Correlation Matrix")
full_lm <- lm(effectiveness ~ ., data=core_data)
print(summary(full_lm))
```

\pagebreak

### Eliminating Coordination
```{r echo=FALSE}
core_data_except_coordination <- subset(core_data, select=-c(coordination))
all_except_coordination <- lm(effectiveness ~ ., data=core_data_except_coordination)
print(summary(all_except_coordination))
```

\pagebreak

### Eliminating Voice Behavior
```{r echo=FALSE}
core_data_except_voice_behavior <- subset(core_data, select=-c(voice_behavior))
all_except_voice_behavior <- lm(effectiveness ~ ., data=core_data_except_voice_behavior)
print(summary(all_except_voice_behavior))
```

\pagebreak

### Eliminating History
```{r echo=FALSE}
core_data_except_history <- subset(core_data, select=-c(history))
all_except_history <- lm(effectiveness ~ ., data=core_data_except_history)
print(summary(all_except_history))
```
\pagebreak

### Eliminating Tenure
```{r echo=FALSE}
core_data_except_tenure <- subset(core_data, select=-c(tenure))
all_except_tenure <- lm(effectiveness ~ ., data=core_data_except_tenure)
print(summary(all_except_tenure))
```
\pagebreak

### Eliminating Team Size
```{r echo=FALSE}
core_data_except_team_size <- subset(core_data, select=-c(team_size))
all_except_team_size <- lm(effectiveness ~ ., data=core_data_except_team_size)
print(summary(all_except_team_size))
```
\pagebreak


### Outcome
Team Size seems to have the least correlation with the Effectiveness, so it is eliminated.

```{r echo=FALSE}
core_data <- subset(core_data, select=-c(team_size))

optimal_subset <- core_data
```

```{r echo=FALSE}
final_model <- lm(effectiveness ~ ., data=core_data)
extract_eq(final_model, wrap = TRUE,use_coefs = TRUE)

```

\pagebreak

## Stage 3: Team Size is Eliminated

### Initial

```{r echo=FALSE}
ggpairs(core_data,progress=FALSE,title="Pairwise Correlation Matrix")
full_lm <- lm(effectiveness ~ ., data=core_data)
print(summary(full_lm))
```
\pagebreak
### Eliminating Coordination
```{r echo=FALSE}
core_data_except_coordination <- subset(core_data, select=-c(coordination))
all_except_coordination <- lm(effectiveness ~ ., data=core_data_except_coordination)
print(summary(all_except_coordination))
```

\pagebreak

### Eliminating Voice Behavior
```{r echo=FALSE}
core_data_except_voice_behavior <- subset(core_data, select=-c(voice_behavior))
all_except_voice_behavior <- lm(effectiveness ~ ., data=core_data_except_voice_behavior)
print(summary(all_except_voice_behavior))
```

\pagebreak

### Eliminating History

```{r echo=FALSE}
core_data_except_history <- subset(core_data, select=-c(history))
all_except_history <- lm(effectiveness ~ ., data=core_data_except_history)
print(summary(all_except_history))
```

\pagebreak

### Eliminating Tenure

```{r echo=FALSE}
core_data_except_tenure <- subset(core_data, select=-c(tenure))
all_except_tenure <- lm(effectiveness ~ ., data=core_data_except_tenure)
print(summary(all_except_tenure))
```
\pagebreak

### Outcome

The elimination of either History or Tenure seems to reduce the goodness of fit of the model. However, eliminating tenure has less negative effect on the model, so it is excluded.

```{r echo=FALSE}
core_data <- subset(core_data, select=-c(tenure))

```

```{r echo=FALSE}
final_model <- lm(effectiveness ~ ., data=core_data)
extract_eq(final_model, wrap = TRUE,use_coefs = TRUE)

```
\pagebreak


## Stage 4: Tenure is Eliminated

### Initial

```{r echo=FALSE}
ggpairs(core_data,progress=FALSE,title="Pairwise Correlation Matrix")
full_lm <- lm(effectiveness ~ ., data=core_data)
print(summary(full_lm))
```

\pagebreak

### Eliminating Coordination

```{r echo=FALSE}
core_data_except_coordination <- subset(core_data, select=-c(coordination))
all_except_coordination <- lm(effectiveness ~ ., data=core_data_except_coordination)
print(summary(all_except_coordination))
```

\pagebreak
### Eliminating Voice Behavior

```{r echo=FALSE}
core_data_except_voice_behavior <- subset(core_data, select=-c(voice_behavior))
all_except_voice_behavior <- lm(effectiveness ~ ., data=core_data_except_voice_behavior)
print(summary(all_except_voice_behavior))
```

\pagebreak

### Eliminating History

```{r echo=FALSE}
core_data_except_history <- subset(core_data, select=-c(history))
all_except_history <- lm(effectiveness ~ ., data=core_data_except_history)
print(summary(all_except_history))
```
\pagebreak

### Outcome 
History has the least correlation with the Effectiveness, so it is eliminated.

```{r echo=FALSE}
core_data <- subset(core_data, select=-c(history))

```
```{r echo=FALSE}
final_model <- lm(effectiveness ~ ., data=core_data)
extract_eq(final_model, wrap = TRUE,use_coefs = TRUE)

```

\pagebreak

## Stage 5: History is Eliminated

### Initial

```{r echo=FALSE}
ggpairs(core_data,progress=FALSE,title="Pairwise Correlation Matrix")
full_lm <- lm(effectiveness ~ ., data=core_data)
print(summary(full_lm))
```
\pagebreak

### Eliminating Coordination

```{r echo=FALSE}
core_data_except_coordination <- subset(core_data, select=-c(coordination))
all_except_coordination <- lm(effectiveness ~ ., data=core_data_except_coordination)
print(summary(all_except_coordination))
```
\pagebreak

### Eliminating Voice Behavior

```{r echo=FALSE}
core_data_except_voice_behavior <- subset(core_data, select=-c(voice_behavior))
all_except_voice_behavior <- lm(effectiveness ~ ., data=core_data_except_voice_behavior)
print(summary(all_except_voice_behavior))
```

\pagebreak

### Outcome

Eliminating Voice Behavior has less detrimental effect on Adjusted R-Sqaured, so it is eliminated.


```{r echo=FALSE}
core_data <- subset(core_data, select=-c(voice_behavior))

```
    
```{r echo=FALSE}
final_model <- lm(effectiveness ~ ., data=core_data)
extract_eq(final_model, wrap = TRUE,use_coefs = TRUE)

```
\pagebreak

## Stage 6: Voice Behavior is Eliminated

At this point, the model only includes one independant variable which is Coordination.

```{r echo=FALSE}
ggpairs(core_data,progress=FALSE,title="Pairwise Correlation Matrix")
full_lm <- lm(effectiveness ~ ., data=core_data)
print(summary(full_lm))
```



\pagebreak

## Results

The table of independant variables in order of their predictive power (highest to lowest) is as follows:


| Rank | Variable |
|------|----------|
| 1 | Coordination |
| 2 | Voice Behavior |
| 3 | History |
| 4 | Tenure |
| 5 | Team Size |
| 6 | Age |
| 7 | Overconfidence |


The optimal model (model with highest adjusted R-Squared) is as follows:

```{r echo=FALSE}
final_model <- lm(effectiveness ~ ., data=optimal_subset)
extract_eq(final_model, wrap = TRUE,use_coefs = TRUE)

```

\pagebreak

# Conclusion



\pagebreak

# Appendix A: Aggregated Data From Teams That Participated
```{r echo=FALSE}

teams
```

\pagebreak

# Appendix B: Data From Actual Survey Responses
```{r echo=FALSE}

responses
```


# Appendix C: R Version
``` {r echo=FALSE}
R.version
```

\pagebreak


# Appendix D: R Packages
``` {r echo=FALSE}
.packages()
```


