---
title: Thesis Survey Data analysis
output: word_document
author: Ashkan Taravati
---
```{r echo=TRUE}
library(GGally)
library(ggplot2)
library(equatiomatic)
library(psych)
library(misty)
library(vtable)
library(ltm)

teams <- read.csv("teams.csv")
responses <- read.csv("responses.csv")
```



```{r echo=TRUE}
# st(responses,
#   vars = c("age", "tenure", "team_history", "overconfidence", "voice"),
#   group = "gender", group.test = TRUE
# )
```
```{r echo=TRUE}
coord_df <- responses[, c("coord_q1", "coord_q2", "coord_q3", "coord_q4", "coord_q5")]
coord_trans_df <- as.data.frame(t(coord_df))
ICC(coord_trans_df)

coord_df$coord_rating <- rowMeans(coord_df)
```

ICC1 is 
```{r echo=TRUE}
multilevel.icc(coord_df$coord_rating, cluster = responses$team, type = 1, method = "aov")
```
ICC2 is
```{r echo=TRUE}
multilevel.icc(coord_df$coord_rating, cluster = responses$team, type = 2, method = "aov")
```
```{r echo=TRUE}
eff_df <- responses[, c("eff_q1", "eff_q2", "eff_q3", "eff_q4", "eff_q5", "eff_q6", "eff_q7", "eff_q8", "eff_q9", "eff_q10")]
eff_trans_df <- as.data.frame(t(eff_df))
ICC(eff_trans_df)

eff_df$eff_rating <- rowMeans(eff_df)
```


ICC1 is
```{r echo=TRUE}
multilevel.icc(eff_df$eff_rating, cluster = responses$team, type = 1, method = "aov")
```
ICC2 is 
```{r echo=TRUE}
multilevel.icc(eff_df$eff_rating, cluster = responses$team, type = 2, method = "aov")
```

H1: Team Overconfidence has a negative effect on team coordination
```{r echo=TRUE} 
lm_overconfidence_coordination <- lm(formula = coordination ~ overconfidence, data = teams)
rep.h1 <- summary(lm_overconfidence_coordination)

print(rep.h1)

plot(teams$coordination ~ teams$overconfidence, data = teams)
abline(lm_overconfidence_coordination)
ggplot(teams, aes(x = coordination, y = overconfidence)) +
  geom_point()
```

H2: Team Coordination has a positive effect on team effectiveness
```{r echo=TRUE}
lm_effectiveness_coordination <- lm(formula = effectiveness ~ coordination, data = teams)
rep.h2 <- summary(lm_effectiveness_coordination)
print(rep.h2)
plot(teams$effectiveness ~ teams$coordination, data = teams)
abline(lm_effectiveness_coordination)
ggplot(teams, aes(x = effectiveness, y = coordination)) +
  geom_point()
```
H3: Voice Behavior has a moderator effect on the relationship between overconfidence and team coordination
```{r echo=TRUE}
inter <- teams$overconfidence * teams$voice_behavior
teams_voice_interaction <- data.frame(teams, inter)
lm_voice_coordination <- lm(formula = coordination ~ overconfidence + voice_behavior + inter, data = teams_voice_interaction)
rep.h3 <- summary(lm_voice_coordination)
rep.h3
plot(teams_voice_interaction$coordination ~ teams_voice_interaction$overconfidence, data = teams_voice_interaction, xlab = "Team Coordination", ylab = "Team Overconfidence")
abline(lm(coordination ~ overconfidence, data = teams_voice_interaction), col = "blue")
abline(lm_voice_coordination, col = "red")
ggplot(teams_voice_interaction, aes(x = coordination, y = overconfidence)) +
  geom_point()
```

Hx1a: Team Overconfidence has a negative effect on team Effectiveness
```{r echo=TRUE}
lm_overconfidence_effectiveness <- lm(formula = effectiveness ~ overconfidence, data = teams)
rep.hx1a <- summary(lm_overconfidence_effectiveness)
print(rep.hx1a)
plot(teams$effectiveness ~ teams$overconfidence, data = teams)
abline(lm_overconfidence_effectiveness)
ggplot(teams, aes(x = effectiveness, y = overconfidence)) +
  geom_point()
```

Hx1b: Team Overconfidence has a reverse effect on team Effectiveness mediated by team Coordination
```{r echo=TRUE}
inter2 <- teams$overconfidence * teams$coordination
teams_overconfidence_interaction <- data.frame(teams, inter2)

lm_overconfidence_effectiveness_coordination <- lm(formula = effectiveness ~ overconfidence + coordination + inter2, data = teams_overconfidence_interaction)
rep.hx1b <- summary(lm_overconfidence_effectiveness_coordination)
print(rep.hx1b)
plot(teams_overconfidence_interaction$effectiveness ~ teams_overconfidence_interaction$overconfidence, data = teams_overconfidence_interaction)
abline(lm_overconfidence_effectiveness_coordination)
ggplot(teams_overconfidence_interaction, aes(x = effectiveness, y = overconfidence)) +
  geom_point()
```
``` {r echo=TRUE}

eff_survey <- subset(responses, select = c(eff_q1, eff_q2, eff_q3, eff_q4, eff_q5, eff_q6, eff_q7, eff_q8, eff_q9, eff_q10))
coord_survey <- subset(responses, select = c(coord_q1, coord_q2, coord_q3, coord_q4, coord_q5))
voice_survey <- subset(responses, select = c(voice_q1, voice_q2, voice_q3, voice_q4, voice_q5, voice_q6))
ovconf_survey <- subset(responses, select = c(ovconf_q1h, ovconf_q1l, ovconf_q2h, ovconf_q2l, ovconf_q3h, ovconf_q3l, ovconf_q4h, ovconf_q4l, ovconf_q5h, ovconf_q5l, ovconf_q6h, ovconf_q6l, ovconf_q7h, ovconf_q7l, ovconf_q8h, ovconf_q8l, ovconf_q9h, ovconf_q9l, ovconf_q10h, ovconf_q10l))
```

Cronbach's Alpha is used to determine the reliability of the survey used for each variable.

```{r echo=TRUE}
cronbach.alpha(eff_survey, CI = TRUE)
```

```{r echo=TRUE}
commit_survey <- eff_survey[1:5]
cronbach.alpha(commit_survey, CI = TRUE)
```

```{r echo=TRUE}
perf_survey <- eff_survey[6:10]
cronbach.alpha(perf_survey, CI = TRUE)
```


```{r echo=TRUE}
cronbach.alpha(coord_survey, CI = TRUE)
```

```{r echo=TRUE}
cronbach.alpha(voice_survey, CI = TRUE)
```

```{r echo=TRUE}
cronbach.alpha(ovconf_survey, CI = TRUE)
```


```{r echo=TRUE}
core_data <- subset(teams, select = -c(team, org, response_rate, response_count))
```

```{r echo=TRUE}
final_model <- lm(effectiveness ~ ., data = core_data)
extract_eq(final_model, wrap = TRUE, use_coefs = TRUE)
```


```{r echo=TRUE}
ggpairs(core_data, progress = FALSE, title = "Pairwise Correlation Matrix")
full_lm <- lm(effectiveness ~ ., data = core_data)
print(summary(full_lm))
```

```{r echo=TRUE}
core_data_except_overconfidence <- subset(core_data, select = -c(overconfidence))
all_except_overconfidence <- lm(effectiveness ~ ., data = core_data_except_overconfidence)
print(summary(all_except_overconfidence))
```

```{r echo=TRUE}
core_data_except_coordination <- subset(core_data, select = -c(coordination))
all_except_coordination <- lm(effectiveness ~ ., data = core_data_except_coordination)
print(summary(all_except_coordination))
```

```{r echo=TRUE}
core_data_except_voice_behavior <- subset(core_data, select = -c(voice_behavior))
all_except_voice_behavior <- lm(effectiveness ~ ., data = core_data_except_voice_behavior)
print(summary(all_except_voice_behavior))
```

```{r echo=TRUE}
core_data_except_history <- subset(core_data, select = -c(history))
all_except_history <- lm(effectiveness ~ ., data = core_data_except_history)
print(summary(all_except_history))
```

```{r echo=TRUE}
core_data_except_tenure <- subset(core_data, select = -c(tenure))
all_except_tenure <- lm(effectiveness ~ ., data = core_data_except_tenure)
print(summary(all_except_tenure))
```

```{r echo=TRUE}
core_data_except_age <- subset(core_data, select = -c(age))
all_except_age <- lm(effectiveness ~ ., data = core_data_except_age)
print(summary(all_except_age))
```

```{r echo=TRUE}
core_data_except_team_size <- subset(core_data, select = -c(team_size))
all_except_team_size <- lm(effectiveness ~ ., data = core_data_except_team_size)
print(summary(all_except_team_size))
```


```{r echo=TRUE}
core_data <- subset(core_data, select = -c(overconfidence))
```

```{r echo=TRUE}
final_model <- lm(effectiveness ~ ., data = core_data)
extract_eq(final_model, wrap = TRUE, use_coefs = TRUE)
```

```{r echo=TRUE}
ggpairs(core_data, progress = FALSE, title = "Pairwise Correlation Matrix")
full_lm <- lm(effectiveness ~ ., data = core_data)
print(summary(full_lm))
```


```{r echo=TRUE}
core_data_except_coordination <- subset(core_data, select = -c(coordination))
all_except_coordination <- lm(effectiveness ~ ., data = core_data_except_coordination)
print(summary(all_except_coordination))
```


```{r echo=TRUE}
core_data_except_voice_behavior <- subset(core_data, select = -c(voice_behavior))
all_except_voice_behavior <- lm(effectiveness ~ ., data = core_data_except_voice_behavior)
print(summary(all_except_voice_behavior))
```


```{r echo=TRUE}
core_data_except_history <- subset(core_data, select = -c(history))
all_except_history <- lm(effectiveness ~ ., data = core_data_except_history)
print(summary(all_except_history))
```

```{r echo=TRUE}
core_data_except_tenure <- subset(core_data, select = -c(tenure))
all_except_tenure <- lm(effectiveness ~ ., data = core_data_except_tenure)
print(summary(all_except_tenure))
```


```{r echo=TRUE}
core_data_except_age <- subset(core_data, select = -c(age))
all_except_age <- lm(effectiveness ~ ., data = core_data_except_age)
print(summary(all_except_age))
```


```{r echo=TRUE}
core_data_except_team_size <- subset(core_data, select = -c(team_size))
all_except_team_size <- lm(effectiveness ~ ., data = core_data_except_team_size)
print(summary(all_except_team_size))
```



```{r echo=TRUE}
core_data <- subset(core_data, select = -c(age))
```
```{r echo=TRUE}
final_model <- lm(effectiveness ~ ., data = core_data)
extract_eq(final_model, wrap = TRUE, use_coefs = TRUE)
```


```{r echo=TRUE}
ggpairs(core_data, progress = FALSE, title = "Pairwise Correlation Matrix")
full_lm <- lm(effectiveness ~ ., data = core_data)
print(summary(full_lm))
```

```{r echo=TRUE}
core_data_except_coordination <- subset(core_data, select = -c(coordination))
all_except_coordination <- lm(effectiveness ~ ., data = core_data_except_coordination)
print(summary(all_except_coordination))
```


```{r echo=TRUE}
core_data_except_voice_behavior <- subset(core_data, select = -c(voice_behavior))
all_except_voice_behavior <- lm(effectiveness ~ ., data = core_data_except_voice_behavior)
print(summary(all_except_voice_behavior))
```
```{r echo=TRUE}
core_data_except_history <- subset(core_data, select = -c(history))
all_except_history <- lm(effectiveness ~ ., data = core_data_except_history)
print(summary(all_except_history))
```

```{r echo=TRUE}
core_data_except_tenure <- subset(core_data, select = -c(tenure))
all_except_tenure <- lm(effectiveness ~ ., data = core_data_except_tenure)
print(summary(all_except_tenure))
```

```{r echo=TRUE}
core_data_except_team_size <- subset(core_data, select = -c(team_size))
all_except_team_size <- lm(effectiveness ~ ., data = core_data_except_team_size)
print(summary(all_except_team_size))
```


Team Size seems to have the least correlation with the Effectiveness, so it is eliminated.

```{r echo=TRUE}
core_data <- subset(core_data, select = -c(team_size))

optimal_subset <- core_data
```

```{r echo=TRUE}
final_model <- lm(effectiveness ~ ., data = core_data)
extract_eq(final_model, wrap = TRUE, use_coefs = TRUE)
```


```{r echo=TRUE}
ggpairs(core_data, progress = FALSE, title = "Pairwise Correlation Matrix")
full_lm <- lm(effectiveness ~ ., data = core_data)
print(summary(full_lm))
```
```{r echo=TRUE}
core_data_except_coordination <- subset(core_data, select = -c(coordination))
all_except_coordination <- lm(effectiveness ~ ., data = core_data_except_coordination)
print(summary(all_except_coordination))
```


```{r echo=TRUE}
core_data_except_voice_behavior <- subset(core_data, select = -c(voice_behavior))
all_except_voice_behavior <- lm(effectiveness ~ ., data = core_data_except_voice_behavior)
print(summary(all_except_voice_behavior))
```

```{r echo=TRUE}
core_data_except_history <- subset(core_data, select = -c(history))
all_except_history <- lm(effectiveness ~ ., data = core_data_except_history)
print(summary(all_except_history))
```


```{r echo=TRUE}
core_data_except_tenure <- subset(core_data, select = -c(tenure))
all_except_tenure <- lm(effectiveness ~ ., data = core_data_except_tenure)
print(summary(all_except_tenure))
```

The elimination of either History or Tenure seems to reduce the goodness of fit of the model. However, eliminating tenure has less negative effect on the model, so it is excluded.

```{r echo=TRUE}
core_data <- subset(core_data, select = -c(tenure))
```

```{r echo=TRUE}
final_model <- lm(effectiveness ~ ., data = core_data)
extract_eq(final_model, wrap = TRUE, use_coefs = TRUE)
```


```{r echo=TRUE}
ggpairs(core_data, progress = FALSE, title = "Pairwise Correlation Matrix")
full_lm <- lm(effectiveness ~ ., data = core_data)
print(summary(full_lm))
```


```{r echo=TRUE}
core_data_except_coordination <- subset(core_data, select = -c(coordination))
all_except_coordination <- lm(effectiveness ~ ., data = core_data_except_coordination)
print(summary(all_except_coordination))
```

```{r echo=TRUE}
core_data_except_voice_behavior <- subset(core_data, select = -c(voice_behavior))
all_except_voice_behavior <- lm(effectiveness ~ ., data = core_data_except_voice_behavior)
print(summary(all_except_voice_behavior))
```

```{r echo=TRUE}
core_data_except_history <- subset(core_data, select = -c(history))
all_except_history <- lm(effectiveness ~ ., data = core_data_except_history)
print(summary(all_except_history))
```

History has the least correlation with the Effectiveness, so it is eliminated.

```{r echo=TRUE}
core_data <- subset(core_data, select = -c(history))
```
```{r echo=TRUE}
final_model <- lm(effectiveness ~ ., data = core_data)
extract_eq(final_model, wrap = TRUE, use_coefs = TRUE)
```


```{r echo=TRUE}
ggpairs(core_data, progress = FALSE, title = "Pairwise Correlation Matrix")
full_lm <- lm(effectiveness ~ ., data = core_data)
print(summary(full_lm))
```


```{r echo=TRUE}
core_data_except_coordination <- subset(core_data, select = -c(coordination))
all_except_coordination <- lm(effectiveness ~ ., data = core_data_except_coordination)
print(summary(all_except_coordination))
```


```{r echo=TRUE}
core_data_except_voice_behavior <- subset(core_data, select = -c(voice_behavior))
all_except_voice_behavior <- lm(effectiveness ~ ., data = core_data_except_voice_behavior)
print(summary(all_except_voice_behavior))
```


Eliminating Voice Behavior has less detrimental effect on Adjusted R-Sqaured, so it is eliminated.


```{r echo=TRUE}
core_data <- subset(core_data, select = -c(voice_behavior))
```
    
```{r echo=TRUE}
final_model <- lm(effectiveness ~ ., data = core_data)
extract_eq(final_model, wrap = TRUE, use_coefs = TRUE)
```



```{r echo=TRUE}
ggpairs(core_data, progress = FALSE, title = "Pairwise Correlation Matrix")
full_lm <- lm(effectiveness ~ ., data = core_data)
print(summary(full_lm))
```

The optimal model:

```{r echo=TRUE}
final_model <- lm(effectiveness ~ ., data = optimal_subset)
extract_eq(final_model, wrap = TRUE, use_coefs = TRUE)
```

```{r echo=TRUE}

teams
```
```{r echo=TRUE}

responses
```


``` {r echo=TRUE}
R.version
```

``` {r echo=TRUE}
.packages()
```


